---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rasterText

<!-- badges: start -->
<!-- badges: end -->

The main goal of `rasterText` is to 
support drawing text in the `rgl` package, but it should
be usable by other packages that need to render text
to a raster.  This can be done through R code or by
direct calls to the underlying C code.

It does just 3 things:  given a vector of strings and 
font descriptions in the format used by `rgl` (which is
very similar to what base R graphics uses), it can:

1.  Measure the strings in terms of pixels.
2.  Pack the strings into a single rectangular region.
3.  Render the strings into a rectangular raster.

## Installation

You can install the development version of rasterText from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("dmurdoch/rasterText")
```

## Example

Here is a simple example:

```{r example}
library(rasterText)

text <- c("abc", "Tokyo (\u6771\u4eac)", "\u6771\u4eac", "abc")

family <- "serif"
font <- 1
cex <- 3

m <- measure_text(text, family, font, cex = cex)
m
p <- pack_text(text, m, max(m[, "width"]))
p
raster <- draw_text_to_raster(text, family, font, cex = cex, measure=m, pack=p)
image(raster)
```
